\section{Vision: A Road-Network Congestion Signal}
\label{sec:vision}

The central claim is not that vehicles should form a fully cooperative swarm. It is that they should expose just enough local traffic state for nearby vehicles to make better independent decisions. This distinction matters for deployment. Command-style V2V coordination creates hard questions about authority, liability, and failure: who tells whom to slow down, which vehicle must occupy a lane, and what happens when messages are delayed? Self-regulating cars should avoid that contract. Each vehicle should remain the sole decision maker for its own motion, and network-level behavior should emerge from repeated local damping rather than from an agreed-upon plan.

\noindent\textbf{Semantic, aggregate exchange.}
We therefore define V2V communication as a bounded semantic API. A sender contributes compact traffic-state summaries, and a receiver aggregates whatever it heard into its own local observation. The API is intentionally lower level than a plan and higher level than raw sensing. It gives a vehicle observability beyond its camera horizon without turning the network into a centralized planner, and without publishing anything that identifies or tracks an individual vehicle. Concretely, the contract admits and forbids two disjoint classes of state:
\begin{itemize}[nosep,leftmargin=1.2em]
\item \textbf{Exchanged:} nearby vehicle counts and density for both AVs and non-AVs, mean speed, lane distribution, local queue estimate, downstream congestion estimate, segment target speed, and merge pressure.
\item \textbf{Never exchanged:} raw video, stable identities, direct acceleration or braking commands, joint lane plans, assignments of AVs to lanes, and coordinated roadblock behavior.
\end{itemize}

\noindent\textbf{Relation to existing connected-vehicle messages.}
Vehicles can already broadcast to one another. Two deployed standards, the SAE J2735 Basic Safety Message (BSM) carried over Dedicated Short-Range Communications (DSRC), and the ETSI Cooperative Awareness Message (CAM) carried over Cellular Vehicle-to-Everything (C-V2X), have each vehicle emit its own position, speed, heading, and path history at up to ten hertz~\cite{sae2020j2735,etsi2019cam,kenney2011dedicated}.
These messages are designed for collision avoidance: they are per-vehicle and centered on the sender, describing where it is and where it is going.
For flow regulation they are a poor fit: a receiver that wants a density or queue estimate must track many senders and fuse their trajectories, which reintroduces per-vehicle identity and linkage and the fusion cost the broadcast was meant to avoid. Our contract takes the complementary position. The unit of exchange is the receiver's neighborhood aggregate, computed over whoever is currently in range, with no sender addressed, retained beyond the freshness window, or reconstructable from the aggregate. Because that aggregate is built from onboard perception as well as received summaries, it naturally covers non-AV (human-driven) vehicles too, not only cooperating AVs. The physical radio can be the same DSRC or C-V2X link; only the message semantics differ.

\noindent\textbf{The contract.}
More formally, vehicle \(i\) maintains a local peer set
\[
N_i(t)=\{j: \mathrm{dist}(i,j) \le R,\; t-\tau_j \le T\},
\]
where \(R\) is the aggregation radius, \(T\) is the freshness horizon, and \(\tau_j\) is the receive time of the latest summary from peer \(j\). The receiver reduces the summaries from \(N_i(t)\) to a single aggregate observation \(a_i(t)=A(\{b_j:j\in N_i(t)\})\), using count sums and confidence-weighted means over fields such as local count, mean speed, density, lane distribution, queue estimate, and merge pressure. The exact radio and aggregation operator can vary, but three semantics should not: expired peers are removed rather than extrapolated, unheard peers map to explicit neutral fields rather than zeros with hidden meaning, and \(a_i(t)\) is advisory evidence rather than a command. In our prototype interface, this substrate is realized as low-rate broadcasts at 2\,Hz, with a 2\,s peer time-to-live (TTL) and a 150\,m radius. This is a stand-in for a DSRC or C-V2X radio, not a claim about a specific one. If no peer is heard, the receiver falls back to neutral values and behaves as a local-only controller; if conflicting summaries arrive, it downweights low-confidence state rather than acting on any single message; and if bandwidth is scarce, it can trade rate or precision while still computing and filtering its own advisory.

\noindent\textbf{Receiver-side semantics and privacy.}
The receiver-side rules are as important as the message format. A self-regulating car treats V2V state as an observation hint, not as authority. The local digital twin records when an aggregate was last refreshed, whether a field came from onboard sensing or V2V, and whether it was neutralized because no peers were heard. This lets the policy distinguish "I see no cooperating vehicles" from "the radio is stale", and lets the safety layer reject advisories that depend on low-confidence state. It also keeps the privacy surface small \emph{by construction}: because the contract's unit is a neighborhood aggregate, a participating vehicle need not publish camera frames, a persistent cross-session identifier, or its own trajectory for its neighbors to benefit from the density and speed information they collectively induce. Realizing that guarantee end to end, so that no raw per-vehicle position ever leaves the sender, is an open problem we return to in Section~\ref{sec:discussion}.

\noindent\textbf{Why aggregate state is enough.}
Highway regulation does not require every vehicle to know the full network state, only early evidence that local flow is approaching a bad operating region: density rising near a merge, queues forming downstream, or speed variance increasing before a shockwave. This suffices because the control objective is physical and local to evaluate. The fundamental diagram relates flow to density, rising to a critical operating point and then collapsing as interactions dominate~\cite{greenshields1935study,lighthill1955kinematic,richards1956shock}; a regulator need only keep density below that threshold and then hold speed high and variance low, and both quantities are precisely what the aggregate signal conveys. A vehicle that damps its own speed variance when it sees rising local pressure removes energy from an incipient wave before it steepens, and when enough vehicles do this independently the stream is held near critical density with no shared plan. Onboard perception supplies immediate headway and leader and follower state, while aggregate V2V fills the blind spots beyond occlusions and around merges, so the observation is local but no longer myopic. The target is thus not consensus but local control under partial information, which is why the communication abstraction, rather than the optimizer, is the central design question.

\noindent\textbf{Relationship to network control.}
The analogy to communication networks is direct: backpressure scheduling stabilizes queues by routing according to local pressure differences~\cite{tassiulas1990stability}, and self-regulating cars seek an analogous pressure signal for physical traffic. The difference is that packets do not brake hard when startled and humans do not obey schedulers, which is why the communication contract must be paired with an ego-centric model of the scene and a safety layer that can reject any unsafe or obstructive advisory.
